---
title: "Text Classifcation"
output: html_document
---
#KNN on TF-IDF  
582,530 abstracts were identified as big data when using TF-IDF to vecotrize the abstracts and KNN as a classifier. 
```{r echo=FALSE}
library(DT)
datatable(read.csv("/home/seh6fy/git/rnd/src/web/short_tf.csv"),options = list(rows.print=3)) 
```
Above can be seen a sample of the abstracts that were identified as big data using TF-IDF. When reading the abstracts, it is clear that some of them are more closely related than others.  
```{r echo=FALSE}
library(DT)
datatable(read.csv("/home/seh6fy/git/rnd/src/web/tf_depart.csv"))
```
The breakdown of department of the abstracts that were identified as big data using TF-IDF is shown above. The vast majority of the abstracts were from HSS which is representative of the proportion of HSS documents in the corpus. 
#KNN on Doc2Vec  
484362 abstracts were idenified as relating to big data by using Doc2Vec to classify the documents and KNN to classify them. 
```{r echo=FALSE}
library(DT)
datatable(read.csv("/home/seh6fy/git/rnd/src/web/short_doc.csv"),options = list(rows.print=3)) 
```
The table above represents a sample of abstracts identified as big data using Doc2Vec. 
```{r echo=FALSE}
library(DT)
datatable(read.csv("/home/seh6fy/git/rnd/src/web/doc_depart.csv"))
```

